### 2020-01-04 Draft/Draft.tex
merge figure 10 and 11

\caption{{\small Detailed properties of the ensembles and their spreads in the ocean and the atmosphere for $\mathsf{m} = 6$ and $t \in [0, 1000]$; note that the \textsf{SCDA} starts from $t > 500$ (shaded green in the central plot) whereas the free run corresponds to $t \leq 500$ (shaded grey). Moreover, the colors of the histograms correspond to the shaded regions in the central plot from where the statistics are derived from, e.g. grey histogram is derived from the statistics gathered during the free run whereas the green histogram corresponds to statistics from the \textsf{SCDA} part of the simulation.}}

@@

{\noindent}In order to maximise the effects of cross-covariance in coupled data assimilation, \citet{lu2015a, lu2015b} suggested that it is advantageous to use leading forecasts and observations in the fast sub-component, i.e. the atmosphere, while updating the slower sub-component, i.e. the ocean, instead of assimilating the instantaneously available atmospheric observation at any time $t$. This suggestion simply follows from figure \ref{fig:3} where we found that the cross-correlation function is maximum when atmosphere leads the ocean, i.e. when $\tau < 0$. This essentially means that the information shared between the oceanic and the atmospheric sub-components in the cross-update may be optimised further by choosing $\tau < 0$, thus maximising the signal-to-noise ratio ({\snr}) in the cross-update. In order to further minimise the effects of noise arising due to stochastic forcing, \citet{lu2015a} used an \tit{average} over some $\tau_\mathsf{win}$ number of leading observations in the atmosphere to update the ocean; they termed this implementation as {\lacc} \citep{lu2015a, lu2015b}. Note that no modification was necessary in reverse, i.e. ocean $\rightarrow$ atmosphere, since the faster sub-component doesn't benefit from any such modification directly. 

@@

\caption{{\small \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{SCDA}/\textsf{LACC} implementations captured by $\delta\boldsymbol{\sigma}_\mathsf{A/O}$; the bottom panel shows the oceanic component while the top panel depicts the atmosphere. Note that the \textsf{SCDA} case depicted in figures \ref{fig:5}--\ref{fig:6} corresponds to $\tau_\mathsf{win} = 1$ in this plot. In other words, \textsf{LACC}$_{[\tau_\mathsf{win} = 1]}$ $\equiv$ \textsf{SCDA}.}}

@@

\centering\includegraphics[width=78mm]{{Fig11}.png}
\caption{{\small \textsf{RMSE} statistics from figure \ref{fig:10} mapped onto a log-scaled ordinal \tit{truth value} space, i.e. \tit{better} or \tit{worse} than the \textsf{WCDA}. In this context, large positive and small negative values are mapped onto `worse' while large negative values are mapped onto `better'; the left panel shows the atmospheric component while the right panel depicts the ocean. The log-scale of the color-map is intended to highlight the local variations.}}
\label{fig:11}
{\noindent}In this paper, we will attempt to quantify the effects of choices of $\tau_\mathsf{win}$ on $\delta\boldsymbol{\sigma}_\mathsf{RMSE}$. It must be noted that the optimal choice of $\tau_\mathsf{win}$ must depend on `$\mathsf{m}$' since $|\taup|$ depends on `$\mathsf{m}$'. Consequently, the results of the {\lacc} implementation compared with the \textsf{WCDA} and the \textsf{SCDA} are shown in figure \ref{fig:10} as a function of `$\mathsf{m}$' and $\tau_\mathsf{win}$. In principle, we expect that for larger scale separations, correspondingly longer leading averaged windows should maximise the cross-component {\snr}, thus leading to a larger disparity between the {\lacc} and the \textsf{WCDA} implementations. However, we note that longer window lengths also decrease the frequency of the coupled cross-updates since this update is made only when preceding $\tau_\mathsf{win}$ observations in the atmosphere become available, which contribute toward diminishing returns of {\lacc} as seen in figure \ref{fig:10}. Overall, we find that the {\lacc} and the \textsf{SCDA} methods perform better than the standard \textsf{WCDA} implementation in the ocean whereas the atmosphere almost always suffers when the coupled cross-updates are included. 

>>>>

\caption{{\small Detailed properties of the ensembles and their spreads in the ocean and the atmosphere for $\mathsf{m} = 6$ and $t \in [0, 1000]$; note that the \textsf{SCDA} starts from $t > 500$ (shaded green in the central plot) whereas the free run corresponds to $t \leq 500$ (shaded grey). Moreover, the colors of the histograms correspond to the shaded regions in the central plot from where the statistics are derived from, e.g. grey histogram is derived from the statistics gathered during the free run whereas the green histogram corresponds to statistics from the \textsf{SCDA} part of the simulation. Note that there are noticeable bi-modalities in the free run and the \textsf{SCDA} histograms -- these non-physical features are due to the inherent spurious cross-correlations in the ensemble-based model error covariance matrix $\mathbf{P}_t^\mathsf{for}$; see figure 4 in \citet{carrassi2018}. Similar spurious cross-correlations would also have been introduced in addition by the ensemble-based observation error covariance matrix $\mathbf{R}$ if we hadn't chosen to use the explicit form \eqref{eq:R} instead.}}

@@

{\noindent}In order to maximise the effects of cross-covariance in coupled data assimilation, \citet{lu2015a, lu2015b} suggested that it is advantageous to use leading forecasts and observations in the fast sub-component, i.e. the atmosphere, while updating the slower sub-component, i.e. the ocean, instead of assimilating the instantaneously available atmospheric observation at any time $t$. This suggestion simply follows from figure \ref{fig:3} where we found that the cross-correlation function is maximum when atmosphere leads the ocean, i.e. when $\tau < 0$. This essentially means that the information shared between the oceanic and the atmospheric sub-components in the cross-update may be optimised further by choosing $\tau < 0$, thus maximising the signal-to-noise ratio ({\snr}) in the cross-update. 

@@

\centering\includegraphics[width=78mm]{{Fig10c}.png}
\caption{{\small \tit{Panel} 1 \tit{and} 2: \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{SCDA}/\textsf{LACC} implementations captured by $\delta\boldsymbol{\sigma}_\mathsf{A/O}$; the bottom panel shows the oceanic component while the top panel depicts the atmosphere. Note that the \textsf{SCDA} case depicted in figures \ref{fig:5}--\ref{fig:6} corresponds to $\tau_\mathsf{win} = 1$ in this plot. In other words, \textsf{LACC}$_{[\tau_\mathsf{win} = 1]}$ $\equiv$ \textsf{SCDA}.\\
\tit{Panel} 3:\textsf{RMSE} statistics from figure \ref{fig:10} mapped onto a log-scaled ordinal \tit{truth value} space, i.e. \tit{better} or \tit{worse} than the \textsf{WCDA}. In this context, large positive and small negative values are mapped onto `worse' while large negative values are mapped onto `better'; the left panel shows the atmospheric component while the right panel depicts the ocean. The log-scale of the color-map is intended to highlight the local variations.}}

@@

{\noindent}In order to further minimise the effects of noise arising due to stochastic forcing, \citet{lu2015a} used an \tit{average} over some $\tau_\mathsf{win}$ number of leading observations in the atmosphere to update the ocean; they termed this implementation as {\lacc} \citep{lu2015a, lu2015b}. Note that no modification was necessary in reverse, i.e. ocean $\rightarrow$ atmosphere, since the faster sub-component doesn't benefit from any such modification directly. In this paper, we will attempt to quantify the effects of choices of $\tau_\mathsf{win}$ on $\delta\boldsymbol{\sigma}_\mathsf{RMSE}$. It must be noted that the optimal choice of $\tau_\mathsf{win}$ must depend on `$\mathsf{m}$' since $|\taup|$ depends on `$\mathsf{m}$'. Consequently, the results of the {\lacc} implementation compared with the \textsf{WCDA} and the \textsf{SCDA} are shown in figure \ref{fig:10} as a function of `$\mathsf{m}$' and $\tau_\mathsf{win}$. We expected and found that for larger scale separations, correspondingly longer leading averaged windows maximise the cross-component {\snr}, thus leading to a larger disparity between the {\lacc} and the \textsf{WCDA} implementations, especially in the slower ocean component -- this is noted in the small yet observable cross-diagonal asymmetry seen in figure \ref{fig:10}. In addition, we also note that longer window lengths decrease the frequency of the coupled cross-updates since this update is made only when preceding $\tau_\mathsf{win}$ observations in the atmosphere become available; this contributes toward diminishing returns of {\lacc} -- this is noticeable in figure \ref{fig:10} where improvement diminishes with increasing averaging window lengths. Overall, we find that the {\lacc} and the \textsf{SCDA} methods perform better than the standard \textsf{WCDA} implementation in the ocean whereas the atmosphere almost always suffers when the coupled cross-updates are included. 
